---
title: "Assignment 4"
author: "Bailey Bradford, Frances Murray, Jonathan Zisk"
date: "2024-04-09"
output:
  html_document:
    theme: cosmo 
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: hide
---

# Assignment 4
1. Discuss with your teammates the tradeoffs in this case between sensitivity and specificity. Write a few sentences that explains the costs and consequences of a model that prioritizes either sensitivity or specificity.

2. Your outcome variable will be a binary variable: Recidivism_Within_3years (you'll need to recode to 1/0).

3. Create plots of continuous and categorical variables that will go into your model. Comment on what you observe in a few sentences.

4. Develop your model (this should be an iterative process where you add and delete features. You'll run the next steps after each model iteration. I only need to know about your best model. I believe that you worked hard and tried everything!).

5. When you are settled on your model, create a nice looking table with the outputs and interpret your results (see the note at the end of last week's lab on interpreting logistic regression coefficients. Also ask google). If you were to summarize who is most at risk for recidivism, what would be the characteristics of that person?

6. Create a ROC curve plot and use that to guide your initial cutoff value (Hint: set labels = TRUE for the geom_roc)

7. Provide your confusion matrix and interpret it. What does each cell mean?

8. What is the accuracy of the model?

9. What is the sensitivity and specificity and what do they mean?

10. Calculate the error for each observation (predicted vs. observed) in your testing dataset. Then, provide some summary statistics by race. Does your model over or under-predict for any group? What about in the case of an intersecting group (race & gender). Determine if your model is equitable for Black Male\Black Female, White Male, White Female?

11. Finally, come up with an estimated\hypothetical cost of keeping someone in prison versus the costs associated with recidivism (arrest, trial, etc.). See if you can do a hypothetical cost-benefit analysis to determine the best threshold value if we were simply doing cold-hearted economic determinants of parole decisions.
Write up a conclusion (use bullet points) on your first assignment for your new job. What do you recommend that policy makers do with your model? 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, cache = TRUE, warning = FALSE, results = "hide")
```


### Discussion of Trade-offs between sensitivity and specificity

- Sensitivity would indicate that the model has a low rate of false negatives (a person is predicted to not reoffend, bud did reoffend). It might be important to keep false negatives low if you have a limited budget or amount of time and want to target resources most heavily towards those who are likely to reoffend. 
- Specificity would indicate that the model low rate of false positives (a person is predicted to reoffend, but did not reoffend). A false positive is dangerous if someone is labeled as a "likely reoffender" and they have greater burdens put on them in a system of parole and probation that is already deeply burdensome and dehumanizing.


```{r load_packages, warning = FALSE}
options(scipen=10000000)

####### CHECK if we need all of the below

library(tidyverse)
library(kableExtra)
library(caret)
library(knitr) 
library(pscl)
library(plotROC)
library(pROC)
library(lubridate)
library(tidycensus)
library(gt)
library(gtExtras)
library(sf)
library(janitor)
library(tigris)
library(RColorBrewer)
library(stargazer)

ga_recid <- read.csv("https://raw.githubusercontent.com/bwbrad/PPA_HW4_Logit/main/Data/NIJ_s_Recidivism_Challenge_Full_Dataset_20240409.csv",
                     na.strings = c(""," ","NA")) %>% 
  clean_names("snake") %>% 
  mutate(recidivism_within_3years = case_when(
           recidivism_within_3years == "true" ~ 1,
           recidivism_within_3years == "false" ~ 0),
         recid_dv_char = case_when(
           recidivism_within_3years == 1 ~ "Reoffended in 3 years",
           recidivism_within_3years == 0 ~ "Did not reoffend in 3 years")) %>% 
  filter(!is.na(percent_days_employed))

recid_sum <- ga_recid %>% 
  group_by(recid_dv_char) %>% 
  summarize(people = n()) %>% 
  mutate(pct_people = people / sum(people))
```


# Choosing Variables

```{r, results = "show"}
gt(recid_sum) %>% 
  fmt_number(columns = people, decimals = 0) %>% 
  fmt_percent(columns = pct_people, decimals = 1) %>% 
  cols_label(recid_dv_char = "Outcome",
             people = "Number",
             pct_people = "Percent") %>% 
  tab_header(title = md("**Overview of justice-involved population**"))
```


### Education Level

People who earned a HS diploma or less are much more represented in those which reoffended in under 3 years, suggesting level of education plays an important role in recidivism rates.

```{r TestIVs_Education}
recid_by_education <- ga_recid %>% 
  group_by(education_level, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

ggplot() +
  geom_col(data = recid_by_education,
           aes(x = education_level, y = justice_inv_pop, fill = education_level),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char) +
  theme_minimal() +
  labs(title = "Recidivism by eductional attainment",
       x = "Level of educational attainment",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```
### Days Worked

The median percent of days employed is much higher for those who did not reoffend. What jumps out particularly is the substantially greater number of reoffenses for people who were employed zero days. This suggests that stability of income and employment may be critical in keeping formerly convicted people out of the justice system.

```{r TestIVs_DaysWorked}
ggplot() +
  geom_histogram(data = ga_recid,
                 aes(x = percent_days_employed, fill = recid_dv_char)) +
  scale_fill_manual(values = c("#1f78b4", "#ff7f00"),
                    guide = "none") +
  geom_vline(data = ga_recid %>%
               filter(recid_dv_char == "Reoffended in 3 years"),
             aes(xintercept = median(percent_days_employed, na.rm = T),
                 colour = "Reoffended in 3 years"),
             lwd = 0.8,
             lty = "longdash",
             show.legend = TRUE) +
  geom_vline(data = ga_recid %>%
               filter(recid_dv_char == "Did not reoffend in 3 years"),
             aes(xintercept = median(percent_days_employed, na.rm = T),
                 colour = "Did not reoffend in 3 years"),
             lwd = 0.8,
             lty = "dotdash",
             show.legend = TRUE) +
  scale_color_manual(name = "Median",
                     values = c("Reoffended in 3 years" = "#ff7f00",
                                "Did not reoffend in 3 years" = "#1f78b4")) +
  scale_y_continuous(labels = scales::label_comma()) +
  scale_x_continuous(labels = scales::label_percent()) +
  facet_wrap(~ recid_dv_char, scales = "free") +
  theme_minimal() +
  labs(title = "Recidivism by % days employed",
       x = "Share of days employed",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### Prison Offense

People who are charged with property offenses are more represented in those which reoffended in under 3 years, suggesting type of prison offense plays an important role in recidivism rates.

```{r TestIVs_PrisonOffense}
recid_by_prisonoffense <- ga_recid %>% 
  group_by(prison_offense, recid_dv_char) %>% 
  summarize(justice_inv_pop = n()) %>% 
  filter(prison_offense != "NA")

ggplot() +
  geom_col(data = recid_by_prisonoffense,
           aes(x = prison_offense, y = justice_inv_pop, fill = prison_offense),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char, scales = "free") +
  theme_minimal() +
  labs(title = "Recidivism by prison offense",
       x = "Prison Offense",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### Prison Years

People who are sentenced to fewer years in prison, specifically fewer than 2 years, are more likely to re-offend in 3 years than those who are given longer prison sentences. 

This might be hard to push, but the high occurrence of people with repeated shorter sentences could suggest that those with lesser offences (assuming lesser offenses = shorter prison sentence) should not be sentenced at all. There could be an alternative intervention for these offenders to keep them out of the prison system for repeated short stints.

```{r TestIVs_PrisonYears, fig.width=6, fig.height=4}
recid_by_PrisonYrs <- ga_recid %>% 
  group_by(prison_years, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

recid_by_PrisonYrs$prison_years <- 
  factor(recid_by_PrisonYrs$prison_years,
         levels = c("Less than 1 year", "1-2 years",
                    "Greater than 2 to 3 years", "More than 3 years"))

x_labs_PrisonYrs <- c("Less than 1 year", "1-2 years",
                      "2-3 years", "More than 3 years")

ggplot() +
  geom_col(data = recid_by_PrisonYrs,
           aes(x = prison_years, y = justice_inv_pop, fill = prison_years),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_x_discrete(labels = x_labs_PrisonYrs) +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char, scales = "free") +
  theme_minimal() +
  labs(title = "Recidivism by prison years",
       x = "Prison years",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### Age at Release

People who are younger at the time of their release are more likely to re-offend within three years. This suggests there needs to be more assistance to reintegrate younger people back into society after their prison release. Without proper social services and sustained behavioral intervention, younger people may be more inclined to fall back into previous behaviors.

```{r TestIVs_ReleaseAge, fig.width=7, fig.height=4}
recid_by_Age <- ga_recid %>% 
  group_by(age_at_release, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

ggplot() +
  geom_col(data = recid_by_Age,
           aes(x = age_at_release, y = justice_inv_pop, fill = age_at_release),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char, scales = "free") +
  theme_minimal() +
  labs(title = "Recidivism by age at release",
       x = "Age at Release",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### Program Attendences

The outlier is that many more people who do not attend any programs during their original sentence are more likely to re-offend in three years. This supports the efforts of prison programming to prevent future offenses. 

Although.......Reoffenses in 3 years is technically higher in every single program attendence category, so I'm not sure how valid this assumption really is...

```{r TestIVs_ProgramAttendance, fig.width=7, fig.height=4}
recid_by_Program <- ga_recid %>% 
  group_by(program_attendances, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

recid_by_Program$program_attendances <- 
  factor(recid_by_Program$program_attendances,
         levels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9",
                    "10", "10 or more"))

ggplot() +
  geom_col(data = recid_by_Program,
           aes(x = program_attendances, y = justice_inv_pop, fill = program_attendances),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char) +
  theme_minimal() +
  labs(title = "Recidivism by program attendances",
       x = "Program attendances",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

## Crafting and assessing a model for recidivism

### Describing the best-performing model

```{r create_partition}
ga_recid <- ga_recid %>% 
  mutate(prison_years_over3 = case_when(
           prison_years == "More than 3 years" ~ 1,
           TRUE ~ 0),
         programs_over10 = case_when(
           program_attendances == "10 or more" ~ 1,
           TRUE ~ 0),
         programs_none = case_when(
           program_attendances == "0" ~ 1,
           TRUE ~ 0),
         older_than37 = case_when(
           age_at_release %in% c("38-42", "43-47", "48 or older") ~ 1,
           age_at_release %in% c("18-22", "23-27", "23-27", 
                                 "28-32", "33-37") ~ 0),
         some_college = case_when(
           education_level == "At least some college" ~ 1,
           education_level %in% c("High School Diploma",
                                  "Less than HS diploma") ~ 0),
         high_supervision = case_when(
           supervision_level_first == "High" ~ 1,
           TRUE ~ 0),
         offense_property = case_when(
           prison_offense == "Property" ~ 1,
           TRUE ~ 0),
         offense_violent_sex = case_when(
           prison_offense == "Violent/Sex" ~ 1,
           TRUE ~ 0),
         one_dependent = case_when(
           dependents == "1" ~ 1,
           TRUE ~ 0),
    )

set.seed(3456)

train_index <- createDataPartition(ga_recid$recidivism_within_3years, p = .50,
                                  list = FALSE,
                                  times = 1)

recid_train <- ga_recid[ train_index,]
recid_test  <- ga_recid[-train_index,]

unique(ga_recid$supervision_level_first)
```

- Creating dummy variables for categorical seem to help
- Jobs per year, average days per drug test, violations fail to report, violations move without permission, made model worse
- A no program attendance variable was not helpful

```{r models}
recid_model_3 <- glm(recidivism_within_3years ~ some_college + offense_property +
                       offense_violent_sex + percent_days_employed +
                       prison_years_over3 + older_than37 + programs_over10 +
                       high_supervision + one_dependent +
                       prior_arrest_episodes_dv_charges + prior_revocations_parole +
                       prior_revocations_probation,
                     data = ga_recid,
                     family="binomial" (link="logit")) 
```


```{r, results = "show"}
stargazer(recid_model_3, type = "text")
```

### Model diagnostics

#### Confusion Matrix

```{r conf_matrix}
recid_test <- recid_test %>% 
  mutate(outcome = as.factor(recidivism_within_3years),
         probs = predict(recid_model_3, recid_test, type= "response"),
         pred_outcome = as.factor(case_when(probs >= 0.5 ~ 1,
                                            probs < 0.5 ~ 0)))

cm <- confusionMatrix(recid_test$pred_outcome, recid_test$outcome,
                      positive = "1")

cm_table <- cm$table
cm_df <- as.data.frame(cm_table)

rownames(cm_df) <- c("True Negative", "False Positive", 
                     "False Negative", "True Positive")
```

66% accuracy, sensitivity of 0.81 and specificity of 0.45

```{r conf_matrix_as_tbl}
gt(cm_df %>% 
     rownames_to_column()) %>% 
  fmt_number(columns = Freq, decimals = 0) %>% 
  tab_header(title = md("**Confusion Matrix**")) %>%
  opt_align_table_header(align = "left") %>%
  cols_label(Freq = "Frequency")
```

#### ROC curve

```{r roc_curve}
auc(recid_test$outcome, recid_test$probs)

ggplot(recid_test, aes(d = as.numeric(outcome), m = probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#1f78b4") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve: Recidivism Model") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)))
```

```{r}
palette2 <- c("#ff7f00","#1f78b4")

ggplot(subset(recid_test, pred_outcome != "NA"), aes(x = probs, fill = as.factor(outcome))) + 
  geom_density(alpha = .75,
               color = NA) +
  scale_fill_manual(name = "Outcome",
                    labels = c("Did not reoffend (0)", "Reoffended (1)"),
                    values = palette2) +
  labs(x = "Recidivism", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", margin = margin(b = 6)),
        strip.text.x = element_text(size = 18))
```

## Prediction error and disparities by race & gender

```{r pred_disparity}
recid_test <- recid_test %>% 
  mutate(cm = case_when((outcome == 1) & (pred_outcome == 1) ~ "True Positive",
                        (outcome == 0) & (pred_outcome == 1) ~ "False Positive",
                        (outcome == 0) & (pred_outcome == 0) ~ "True Negative",
                        (outcome == 1) & (pred_outcome == 0) ~ "False Negative"),
         gender = case_when(gender == "F" ~ "Women",
                            gender == "M" ~ "Men"),
         race = case_when(race == "BLACK" ~ "Black",
                          race == "WHITE" ~ "White"))

error_by_demographics <- recid_test %>% 
  group_by(gender, race, cm) %>% 
  tally() %>% 
  mutate(pct_outcome = n / sum(n))

gt(error_by_demographics) %>% 
  fmt_number(columns = n, decimals = 0) %>% 
  fmt_percent(columns = pct_outcome, decimals = 1) %>% 
  cols_label(cm = "Prediction Category",
             n = "Count",
             pct_outcome = "% Subgroup") %>% 
  tab_header(title = md("**Prediction disparities by race & gender**")) %>%
  opt_align_table_header(align = "left") %>% 
  tab_style(location = cells_row_groups(),
            style = cell_text(weight = "bold"))
```

## Estimating a "cost" of recidivism











# Appendix
Residence changes does not really suggest housing instability is related to recidivism. Nor is gang affiliation (not listed below).
```{r TestIVs_ResidenceChanges}
recid_by_moving <- ga_recid %>% 
  group_by(residence_changes, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

ggplot() +
  geom_col(data = recid_by_moving,
           aes(x = residence_changes, y = justice_inv_pop, fill = residence_changes),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char) +
  theme_minimal() +
  labs(title = "Recidivism by number of residence changes",
       x = "Number of residence changes",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

Episodes of prior gun charges doesn't predict recidivism in 3 years either.
```{r TestIVs_PriorGunCharges}
recid_by_PriorGun <- ga_recid %>% 
  group_by(prior_arrest_episodes_gun_charges, recid_dv_char) %>% 
  summarize(justice_inv_pop = n())

ggplot() +
  geom_col(data = recid_by_PriorGun,
           aes(x = prior_arrest_episodes_gun_charges, y = justice_inv_pop, fill = prior_arrest_episodes_gun_charges),
           position = "dodge",
           show.legend = FALSE) +
  scale_fill_brewer(type = "qual",
                    palette = "Paired") +
  scale_y_continuous(labels = scales::label_comma()) +
  facet_wrap(~ recid_dv_char) +
  theme_minimal() +
  labs(title = "Recidivism by episodes of prior gun charges",
       x = "Episodes of prior gun charges",
       y = "Justice-involved pop.") +
  theme(plot.title = element_text(face = "bold", margin = margin(b = 6)),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```